---
title: "Predicting cocktail categories with tidymodels and textrecipes"
author: "Jamie Ralph"
date: "29/05/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidymodels)
library(textrecipes)
library(vip)

```

## Load the data, create binary category, and collapse ingredients

```{r}
boston_cocktails <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-26/boston_cocktails.csv')

cocktails_parsed <- boston_cocktails %>%
    mutate(category = case_when(category != "Cocktail Classics" ~ "other",
                                TRUE ~ "classic")) %>%
    group_by(category, name) %>%
    summarise(ingredient = toString(ingredient)) %>%
    mutate(ingredient = str_to_lower(ingredient)) %>%
    ungroup() %>%
    select(category, ingredient)
```

## Prepare train and test sets

```{r}
set.seed(123)

cocktails_split <- initial_split(cocktails_parsed, p = 0.8, strata = category)

cocktails_train <- training(cocktails_split)
cocktails_test <- testing(cocktails_split)
```

## Prepare classification recipe

```{r}
cocktails_recipe <- recipe(category ~ ingredient, data = cocktails_train) %>%
    step_tokenize(ingredient) %>%
    step_stopwords(ingredient) %>%
    step_tfidf(ingredient) %>%
    step_normalize(all_predictors())

cocktails_prep <- prep(cocktails_recipe)
```

## Define lasso regression specification and model workflow

```{r}
lasso_spec <- logistic_reg(penalty = tune(), mixture = 1) %>%
    set_engine("glmnet")

lasso_wf <- workflow() %>%
    add_recipe(cocktails_recipe) %>%
    add_model(lasso_spec)
```

## Define bootstrap resampling, tune model, and visualise results

```{r}
lambda_grid <- grid_regular(penalty(), levels = 50)

cocktail_folds <- bootstraps(cocktails_train, strata = category)

lasso_grid <- tune_grid(
    lasso_wf,
    resamples = cocktail_folds,
    grid = lambda_grid,
    metrics = metric_set(roc_auc, ppv, npv)
)

bstrap_results <- lasso_grid %>%
    collect_metrics() %>%
    ggplot(aes(penalty, mean, color = .metric)) +
    geom_line(size = 1.5, show.legend = FALSE) +
    facet_wrap(~.metric) +
    scale_x_log10()

bstrap_results

```

## Finalise the workflow with best AUC and pull out important variables

```{r}
best_auc <- lasso_grid %>%
    select_best("roc_auc")

final_lasso <- finalize_workflow(lasso_wf, best_auc)

vi_plot <- final_lasso %>%
    fit(cocktails_train) %>%
    pull_workflow_fit() %>%
    vi(lambda = best_auc$penalty) %>%
    group_by(Sign) %>%
    top_n(20, wt = abs(Importance)) %>%
    ungroup() %>%
    mutate(
        Importance = abs(Importance),
        Variable = str_remove(Variable, "tfidf_ingredient_"),
        Variable = fct_reorder(Variable, Importance)
    ) %>%
    ggplot(aes(x = Importance, y = Variable, fill = Sign)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Sign, scales = "free_y") +
    labs(y = NULL)

vi_plot
```

## Use last fit on test set and collect metrics

```{r}
cocktails_final <- last_fit(final_lasso, cocktails_split)

cocktails_final %>% 
    collect_metrics()

cocktails_final %>% 
    collect_predictions() %>%
    conf_mat(category, .pred_class)
```

